### 2018-06-19 doc/latex/03-Simulator.tex
Add Calibrator doc

>>>>

The Calibrator is a tool designed to calibrate the scenario tests.
It can also be used for running a simulation multiple times to gather statistical data.
This data can then be written to a file or be used for generating boxplots.
The following configuration options are available:

\begin{description}
    \item[\texttt{--config}] \ \\
        Specifies the run configuration parameters to be used for the simulation.
        If this is provided multiple times, the calibration is performed on all given simulations.
        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
    \item[\texttt{--testcases}] \ \\
        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
    \item[\texttt{--multiple}]\ \\
        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
    \item[\texttt{--single}]\ \\
        Run the simulations with the fixed seeds to determine the exact values.
    \item[\texttt{--output}]\ \\
        Write the results of the calibration to a file with given filename. This resulting file contains ...
    \item[\texttt{--write}]\ \\
        Write boxplots to files in the current directory. This creates an image for each config or testcase.
    \item[\texttt{--display}]\ \\
        Display the boxplots for the last step.
    \item[\texttt{--displayStep}]\ \\
        Display the boxplots for a specified step.
\end{description}

Examples:\\
To find the exact values for the testcases and write these to a file:\\

\centerline{\texttt{calibration -s -o out.json}}

To run a configuration file 10 times with a random seed and display the generated boxplot for the last step in the simulation:\\

\centerline{\texttt{calibration -c run\_default.xml -m 10 -d}}

To run the testcase \texttt{influenza\_a} 10 times, write the results to a file and for each step in the simulation write a boxplot to a file:\\

\centerline{\texttt{calibration -t influenza\_a -m 10 -w -o out.json}}
